Holomorphic field theories and higher algebra

### 2022-10-03 draft.tex
stupid macros

\begin{lmm}
The action of $\sl(3)$ on $\cT_{\sfE}(F,N)$ and $\cT_{\sfM}(F,\check{N})$ extends to their quantizations.
\end{lmm}

@@

A beautiful maneuver of physics is compactification, where one takes a field theory $\cT$ in $n$ dimensions and produces a field theory $\cT_N$ in $k$ dimensions by studying $\cT$ on manifolds of the form $N \times \Sigma$, where $\Sigma$ is $k$-dimensional.
A close cousin is dimensional reduction, where one restricts to solutions of the classical field theory that are constant along $N$.
We have already worked with a factorization algebra version of these maneuvers: 
pushing forward along the map $\rho: \C^\times \times \CC^\times \to \RR_{>0} \times \RR_{>0}$ that sends $(z_1,z_2)$ to $(|z_1|, |z_2|)$.
For a holomorphic factorization algebra $\cF$, the pushforward $\rho_* \cF$ is locally constant on $\RR_{\geq 0}^2 \cong \RR^2$, and hence it encodes an $E_2$-algebra.
We now apply this result in the context of holomorphic QCD and see what Seiberg duality would mean.

\begin{lmm}
For a holomorphic QCD theory, this compactification is a Landau-Ginzburg B-model for \owen{finish! would it be easier just to spell out what happens to matter, gauge, and the QCD?}
\end{lmm}

>>>>

\begin{lem}
The action of $\sl(3)$ on $\cT_{\sfE}(F,N)$ and $\cT_{\sfM}(F,\check{N})$ extends to their quantizations.
\end{lem}

@@

A beautiful maneuver of physics is compactification, where one takes a field theory $\cT$ in $n$ dimensions and produces a field theory $\cT_N$ in $k$ dimensions by studying $\cT$ on manifolds of the form $N \times \Sigma$, where $\Sigma$ is $k$-dimensional.
A close cousin is dimensional reduction, where one restricts to solutions of the classical field theory that are constant along $N$.
We have already worked with a factorization algebra version of these maneuvers: 
pushing forward along the map $\rho: \CC^\times \times \CC^\times \to \RR_{>0} \times \RR_{>0}$ that sends $(z_1,z_2)$ to $(|z_1|, |z_2|)$.
For a holomorphic factorization algebra $\cF$, the pushforward $\rho_* \cF$ is locally constant on $\RR_{\geq 0}^2 \cong \RR^2$, and hence it encodes an $E_2$-algebra.
We now apply this result in the context of holomorphic QCD and see what Seiberg duality would mean.

\begin{lem}
For a holomorphic QCD theory, this compactification is a Landau-Ginzburg B-model for \owen{finish! would it be easier just to spell out what happens to matter, gauge, and the QCD?}
\end{lem}
